### 2018-08-29 paper/conclusion.tex
Improvements according to Ana's questions and suggestions.
updates
Discussion of adaptive test cases added

\section{Conclusion}
\label{sec:conc}
% ==============================================================================

@@

>>>>

\section{Discussion}
\label{sec:conc}
% ==============================================================================
\subsubsection*{Discussion of Fault Domains}

% ==============================================================================
\subsubsection*{Discussion of Adaptive Test Cases}
The tests suggested 
in~\cite{Hennessy:1988:ATP:50497,DBLP:conf/icfem/CavalcantiG07} were \emph{preset} in the
sense that the trace to be executed was pre-defined for each test. As a consequence,
the authors of~\cite{DBLP:conf/icfem/CavalcantiG07} introduced \emph{inconclusive}
as a third test result, applicable to the situations where the intended trace
of the execution was blocked, due to legal, but nondeterministic behaviour of the
SUT. In contrast to that, 
our test cases
specified in Section~\ref{sec:finitecompletefails} and \ref{sec:finitecomplete} are
adaptive. This has the advantage that test executions $(Q\parallel[\Sigma] U_F(p))$
for failures refinement
will never block before the final step specified by branch (\ref{eq:ufd}). As
a consequence, we do not need inconclusive test results. It should be noted, however,
that it is necessary for our test verdicts to recognise also deadlocks in the final
test step and interpret 
them as FAIL, as described in Section~\ref{sec:finitecompletefails}. In practice,
this is realised by adding a timeout event to the testing environment which indicates
deadlock situations. For real-time systems, this is an accepted technique, because
the SUT has to respond within a pre-defined latency interval, otherwise its behaviour 
is considered to be blocked and regarded as a failure. Our tests executions 
$(Q\parallel[\Sigma] U_T(p))$ for trace refinement never block at all. The adaptive       
behaviour of our test cases, however, induce the obligation to check that {\it all}
possible executions have been performed before the test can be considered as passed.
Typically, it is therefore assumed that a 
\emph{complete testing assumption}~\cite{hierons_testing_2004} holds which means that
every possible behaviour of the SUT has been performed after a finite number of
test executions. 
In practice, this is realised by executing each test several times, 
recording the traces that have been performed, and using hardware or software coverage 
analysers to determine whether all possible test execution behaviours of the SUT
have been observed. Therefore, the application of adaptive test cases comes at the price
of having to apply some grey-box testing techniques enabling us to decide whether
all SUT behaviours have been observed.

% ==============================================================================
\subsubsection*{Implications for CSP Model Checking}

% ==============================================================================
\subsubsection*{Conclusion}

@@

\paragraph{Acknowledgements}
The authors would lime to thank Bill Roscoe and Thomas Gibson-Robinson for their advice on using the FDR4 model checker and for very helpful discussions concerning the potential implications of this paper in the field of model-checking.
